Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-11 paper.qmd
Updated Figure 14

error_plot_pbmc <- ggplot(error_pbmc, 
                          aes(x = a1, 
                              y = MSE, 
                              colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_pbmc$a1))[c(1, 5, 9, 13, 17, 21, 26)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a','#ff7f00',
                              '#984ea3','#999999','#a65628','#f781bf')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

@@

nldr_mnist1 <- tsne_mnist |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  interior_annotation("a", c(0.08, 0.93))

@@

nldr_mnist2 <- umap_mnist |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("b")

@@

nldr_mnist3 <- phate_mnist |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour='#377eb8') +
  interior_annotation("c")

@@

nldr_mnist4 <- trimap_mnist |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("d")

@@

nldr_mnist5 <- pacmap_mnist |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("e")
```

@@

error_plot_mnist <- ggplot(error_mnist, 
                          aes(x = a1, 
                              y = MSE, 
                              colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_mnist$a1))[append(seq(1, length(unique(error_mnist$a1)), by = 5), 24)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a', "#ff7f00",'#a65628')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

>>>>

error_plot_pbmc <- ggplot(error_pbmc, 
                          aes(x = a1, 
                              y = MSE, 
                              colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_pbmc$a1))[c(1, 5, 9, 13, 17, 21, 26)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a','#ff7f00',
                              '#984ea3','#999999','#a65628','#f781bf')) +
  scale_y_log10() +
  ylab("MSE") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

@@

nldr_mnist1 <- tsne_mnist |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  interior_annotation("a", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

@@

nldr_mnist2 <- umap_mnist |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("b") +
  theme(aspect.ratio = 1)

@@

nldr_mnist3 <- phate_mnist |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour='#377eb8') +
  interior_annotation("c") +
  theme(aspect.ratio = 1)

@@

nldr_mnist4 <- trimap_mnist |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("d") +
  theme(aspect.ratio = 1)

@@

nldr_mnist5 <- pacmap_mnist |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("e") +
  theme(aspect.ratio = 1)
```

@@

error_plot_mnist <- ggplot(error_mnist, 
                          aes(x = a1, 
                              y = MSE, 
                              colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_mnist$a1))[append(seq(1, length(unique(error_mnist$a1)), by = 5), 24)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a', "#ff7f00",'#a65628')) +
  scale_y_log10() +
  ylab("MSE") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))
